Why robot programming is hard

### 2014-08-26 paper.tex
More references

The difficulty of this programming task depends on several factors:

@@

\item {\bf Goal specification}: some tasks are easy to describe, such as navigation goals specified by a single point in 3-dimensional space. Other goals, such as washing the dishes or tidying up, are more difficult to specify. Successful completion may be more dependent on how exactly the robot performs the task. Generally speaking, the more difficult it is to frame the goal specification, the more difficult the programming task will be.
% REF: something from the EUP literature?

\item {\bf Amount of autonomy}: robots are gaining the ability to perform some functions autonomously, such as spatial navigation and object manipulation.  The less autonomy exhibited by the robot, the easier it is to program the robot, because increased autonomy requires the programmer to develop more complex mental models of the robot's perceptions and behavior. Teleoperation interfaces are fairly easy to use because there is generally a one-to-one mapping between the user's inputs and the robot's behavior. Once a robot starts to act autonomously, understanding its behavior (and debugging it!) becomes more challenging.
\end{itemize}

>>>>

Many of the lessons learned from the fields of end user programming~\cite{dontcheva-nocode} and end user software engineering~\cite{ko-acm11} also apply to robot programming, though robots' physical embodiment leads to additional challenges. I believe that the difficulty of the robot programming task boils down to several factors:

@@

\item {\bf Goal specification}: some tasks are easy to describe, such as navigation goals specified by a single point in 3-dimensional space. Other goals, such as washing the dishes or tidying up, are more difficult to specify. Successful completion may be more dependent on how exactly the robot performs the task. Generally speaking, the more difficult it is to frame the goal specification, the more difficult the programming task will be~\cite{ko-vlhcc04}.
% REF: something from the EUP literature?

\item {\bf Amount of autonomy}: robots are gaining the ability to perform some functions autonomously, such as spatial navigation and object manipulation.  The less autonomy exhibited by the robot, the easier it is to program the robot, because increased autonomy requires the programmer to develop more complex mental models of the robot's perceptions and behavior~\cite{kulesza-chi12}. Teleoperation interfaces are fairly easy to use because there is generally a one-to-one mapping between the user's inputs and the robot's behavior. Once a robot starts to act autonomously, understanding its behavior (and debugging it!) becomes more challenging.
\end{itemize}
